Gray-Box Optimization using the Parameter-less Population Pyramid

### 2015-04-02 Gray Box Optimization using the Parameter-less Population Pyramid/main.tex
Fixed copyright and updated style file

\permission{Permission to make digital or hard copies of all or part of this work
for personal or classroom use is granted without fee provided that copies are not
made or distributed for profit or commercial advantage and that copies bear this
notice and the full citation on the first page. Copyrights for components of this
work owned by others than ACM must be honored. Abstracting with credit is permitted.
To copy otherwise, or republish, to post on servers or to redistribute to lists,
requires prior specific permission and/or a fee. Request permissions from permissions@acm.org.}
\conferenceinfo{GECCO'15,} {July 11-15, 2015, Madrid, Spain.}
\CopyrightYear{2015}
\crdata{TBA}
\clubpenalty=10000
\widowpenalty = 10000

>>>>

\setcopyright{acmcopyright}
\conferenceinfo{GECCO '15,}{July 11 - 16, 2015, Madrid, Spain}
\isbn{978-1-4503-3472-3/15/07}\acmPrice{\$15.00}

\doi{http://dx.doi.org/10.1145/2739480.2754775}
\clubpenalty=10000
\widowpenalty = 10000
